JATOSをDockerを使ってサーバーに導入する方法

### 2023-04-09 how-to-jatos-web.Rmd
update

```
sudo apt install \
    apt-transport-https \
    ca-certificates \
    curl \
    gnupg-agent \
    software-properties-common
```

```
curl -fsSL https://download.docker.com/linux/ubuntu/gpg | sudo apt-key add -
```

```
sudo apt-key fingerprint 0EBFCD88
```

@@

```
sudo apt install docker-ce docker-ce-cli containerd.io
```

@@

```
sudo curl -L "https://github.com/docker/compose/releases/download/1.24.0-rc1/docker-compose-$(uname -s)-$(uname -m)" -o /usr/local/bin/docker-compose

sudo chmod +x /usr/local/bin/docker-compose

sudo ln -s /usr/local/bin/docker-compose /usr/bin/docker-compose
```

@@

```
sudo docker-compose -f /opt/traefik/docker-compose.yml up -d
```

@@

>>>>

```
sudo apt-get install \
    ca-certificates \
    curl \
    gnupg
```

```
sudo mkdir -m 0755 -p /etc/apt/keyrings
curl -fsSL https://download.docker.com/linux/ubuntu/gpg | sudo gpg --dearmor -o /etc/apt/keyrings/docker.gpg
```

```
echo \
  "deb [arch="$(dpkg --print-architecture)" signed-by=/etc/apt/keyrings/docker.gpg] https://download.docker.com/linux/ubuntu \
  "$(. /etc/os-release && echo "$VERSION_CODENAME")" stable" | \
  sudo tee /etc/apt/sources.list.d/docker.list > /dev/null
```

@@

```
echo \
  "deb [arch="$(dpkg --print-architecture)" signed-by=/etc/apt/keyrings/docker.gpg] https://download.docker.com/linux/ubuntu \
  "$(. /etc/os-release && echo "$VERSION_CODENAME")" stable" | \
  sudo tee /etc/apt/sources.list.d/docker.list > /dev/null
```

```
sudo apt-get update
```

```
sudo apt-get install docker-ce docker-ce-cli containerd.io docker-buildx-plugin docker-compose-plugin
```

@@

```
sudo apt install docker-compose-plugin
```

@@

```
sudo docker compose -f /opt/traefik/docker-compose.yml up -d
```

@@

設定できたら，Docker composeで

```
sudo docker compose -f dir_docker_compose/jatos/docker-compose.yml up -d
```
